---
output:
  pdf_document:
    toc : true
params:
  MCMC  : NA
  userfile  : NA
  camsta  : NA

header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage[table]{xcolor}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}

---

---
title: `r paste0("Calibration Report for ", params$camsta)`
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
options(knitr.table.format = "latex")
library(kableExtra)
source("OmexCal_Load.R")
source(params$userfile)
```
# MCMC

## Profiles

```{r, echo=FALSE, warning=FALSE, fig.height=6}

pProfs<-MCProfPlot(MCMC, TRUE)

print(pProfs)
```

\pagebreak

## Fluxes

Fluxes at the sediment-water interface (positive upwards). Available observations are indicate as ranges on the plots.
The curve indicates the probability density of Fluxes inferred from the MCMC procedure.

```{r, echo=FALSE, warning=FALSE, fig.height=5}
pl<-MCFluxPlot(MCMC, TRUE)
pl
```

\pagebreak

## MicroProfiles

```{r, echo=FALSE, warning=FALSE, fig.height=6}
pl[[2]]
```


\pagebreak

## Parameters

!! Parameters values are not converted to "print" value for now .. 


```{r, echo=FALSE, warning=FALSE, fig.height=5}
pl<-MCParsPlot(MCMC, TRUE)
pl
```

\pagebreak

## Misfits

...