---
output:
  pdf_document:
    toc : true
params:
  Parlist   : NA
  Costlist  : NA
  userfile  : NA
  camsta  : NA

header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage[table]{xcolor}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
---

---
title: `r paste0("Calibration Report for ", params$camsta)`
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
options(knitr.table.format = "latex")
library(kableExtra)
setwd('../')
source("Utils/OmexCal_Load.R")
source(params$userfile)
```
# Stepwise calibration

## Profiles

```{r, echo=FALSE, warning=FALSE, fig.height=6}
rn<-c("Guess",stepNames,"Final")
runnames=factor(rn,levels=rn,ordered=T)
Simplot(Parlist,TRUE,runnames = runnames)+ggtitle(paste(sta,"_",cam,"1"))
```

\pagebreak

## Fluxes

Fluxes at the sediment-water interface (positive upwards). Available observations are indicate as ranges on the plots.

```{r, echo=FALSE, warning=FALSE, fig.height=5}
Fluxplot(Parlist,TRUE,runnames = runnames)+ggtitle(paste(sta,"_",cam,"1"))
```

\pagebreak

## MicroProfiles

```{r, echo=FALSE, warning=FALSE, fig.height=6}
if (!is.null( unlist(MLIST) )) { 
SimplotMicro( Parlist, TRUE, YL=1, runnames = runnames) + ggtitle(paste(sta,"_",cam,"1"))
}
```

\pagebreak

## Parameters

### Values
*"* in the table means that the parameter is same as in the previous column. 

Highlighted in red are parameter values that are close to the minimum/maximum, indicating that the calibration procedure is somehow "blocked" by the ranges imposed on those parameters.

```{r, echo=FALSE, warning=FALSE, fig.height=5}
bo<-lapply(Parlist, function (p){
  pdf<-subset(partableplot(p, tableoutput = FALSE), select="Cal.")
})

for (i in 1:length(bo)){
    colnames(bo[[i]])<-runnames[i]
}

allpdfs<-do.call(cbind,bo)
allpdfs$units<-"-"
allpdfs$min<-"-"
allpdfs$max<-"-"

allpdfs[ intersect(rownames(allpdfs),rownames(parsdfforprint)),c("units","min","max")]<-
  format(parsdfforprint[intersect(rownames(allpdfs),rownames(parsdfforprint)), c("unit","min","max")], digits = 3,nsmall=0,scientific=F,drop0trailing=T)

for (ir in (length(stepNames)+2):2) {
  for (jr in (1:nrow(allpdfs))){
    if (allpdfs[jr,ir]==allpdfs[jr,ir-1]) {allpdfs[jr,ir]=" \" "}
    if ((rownames(allpdfs)[jr]%in% unlist(PLIST)) && ( allpdfs[jr,ir]!=" \" ")){
      if ((abs( as.numeric(allpdfs[jr,ir])- as.numeric(allpdfs[jr,"min"]))
          /( .5*(as.numeric(allpdfs[jr,ir])+as.numeric(allpdfs[jr,"min"]))+1e-14)<0.02)|(
            abs(as.numeric(allpdfs[jr,ir])- as.numeric(allpdfs[jr,"max"]))/
              (.5*(as.numeric(allpdfs[jr,ir])+as.numeric(allpdfs[jr,"max"])))<0.02))
      {
        allpdfs[jr,ir]    <- cell_spec( allpdfs[jr,ir] ,"latex", color ="red")
          }
    }
  }
}




kable(allpdfs,booktabs=T,longtable=T, escape=F) %>% 
  kable_styling(latex_options = "striped")
 
```

### Sensitivity

The next figure represents the model cost's sensitivity to perturbation of the parameters around their final calibrated value. 
In short the higher the metric, the most this parameter is having a high impact on the overall model misfit metric.

```{recho=FALSE, warning=FALSE}

  parSta<-Parlist[[length(Parlist)]]

  Sens <- sensFun(func=OCOST_GEN,
                  parms=parSta[unique(unlist(PLIST))],
                  Vlist=unique(unlist(VLIST)),
                  Flist=unique(unlist(FLIST)),
                  Mlist=unique(unlist(MLIST))
                  )

  sS<-summary(Sens)
  sS$param<-rownames(sS)
  sS$param <- factor(sS$param, levels = sS$param[order( sS$L1,decreasing = T)])
  
  g1<-ggplot(as.data.frame(sS),aes(x=param,y=L1))+geom_point()
  print(g1)
```

\pagebreak

## Misfits

The variables cost are estimated as the sum of squared weighted residuals for each: 

$$\mathcal{C}_j=\sum\limits_{i=1}^{n_{obs,j}} \frac{Model_i- Obs_i}{Err_i}$$

```{r, echo=FALSE}

dfSSR<-do.call(cbind,lapply(Costlist, function(d){d[,"SSR"]}))
colnames(dfSSR)<-runnames
rownames(dfSSR)<-Costlist[[1]][,"name"]

ggplot(melt(dfSSR), aes(x=Var2, y=value, color=Var2))+
  geom_point(size=2)+
  facet_wrap(~Var1, scales = "free")+
  ylab("Variables Costs")+
  xlab("Calibration Steps")+
  scale_color_brewer(palette = "RdYlGn", name="Calibration Steps")+
  theme_bw()+theme(legend.position = "none")

#kable(dfSSR)
```

The model cost is the scaled sum of variable costs: 

$$\mathcal{C}=\sum\limits_{j=1}^{n_{var}}\frac{\mathcal{C}_j}{n_{obs,j}}$$

Here the total height of each bar indicate the model cost, while colored fraction of the bar indicate the contribution of each type of observations in the model cost.


```{r, echo=FALSE, fig.height=4}
dfModCost <- do.call(cbind,lapply(Costlist, function(d){ d[,"SSR"]*d[,"scale"]  }))
colnames(dfModCost)<-runnames
rownames(dfModCost)<-Costlist[[1]][,"name"]

ggplot(melt(dfModCost), aes(x=Var2, y=value,fill=Var1))+
  geom_bar( stat="identity")+
  ylab("Model Cost")+
  xlab("Calibration Steps")+
  theme_bw()+scale_fill_discrete(name="Var. Costs")

#kable(dfModCost)
# We could consider to add color to the cells 
```



