---
output:
  pdf_document:
    toc : true
params:
  MCMC      : NA
  userfile  : NA
  cam       : NA
  sta       : NA

header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
#- \usepackage[table]{xcolor}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}

---

---
title: `r paste0("MCMC Calibration Report for ", params$sta," - ", params$cam )`
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
options(knitr.table.format = "latex")
#library(kableExtra)
setwd('../')
source("Utils/OmexCal_Load.R")
source(params$userfile)

parSta      <<- OmexCal_AdaptForSta(pars,station = sta, campaign = cam)

```
# Convergence

```{r Conv, echo=FALSE, warning=FALSE, fig.height=6, fig.show='asis'}

plot(MCMC, Full=TRUE, ask=FALSE )


#plot(MCMC, Full=TRUE, ask=FALSE, which=NULL)
```


# Profiles

```{r Profs, echo=FALSE, warning=FALSE, fig.height=6}

pProfs<-MCProfPlot(MCMC, TRUE,YL=max(dfProfiles$LowerDepth, na.rm = TRUE))
print(pProfs$pProfs)

```

\pagebreak

## Fluxes

Dissolved fluxes at the sediment-water interface (positive upwards), and integrated diagnostics.
Available observations are indicate as ranges on the plots.
The curves indicate the probability density distributions inferred from the MCMC procedure.

```{r Fluxes, echo=FALSE, warning=FALSE, fig.height=5}

pl<-MCFluxPlot(MCMC, plotdata = any(!is.na(dfFluxes$value)))
pl

```

\pagebreak

## MicroProfiles

```{r MicroProfiles, echo=FALSE, warning=FALSE, fig.height=6}

print(pProfs$pMicro)

```


\pagebreak

## Parameters

!! Parameter values are not converted to "print" value yet .. 

```{r Parameters, echo=FALSE, warning=FALSE, fig.height=5}

pl<-MCParsPlot(MCMC, TRUE)
pl

# Reducing the MCMC size
MCMCr<- MCMC  
NumRun<-2000

if(!is.null(NumRun)){
  NLINES <- max(length(MCMC$SS),NumRun)
  # not sure which best way to select within the MCMC
  if (TRUE){
    inds <- which(MCMC$SS <= quantile(MCMC$SS,NumRun/NLINES))
  }else{
    inds <-  (length(MCMC$SS)-NumRun): length(MCMC$SS)    
    }
  MCMCr$pars  <- MCMC$pars  [inds,]
  MCMCr$SS    <- MCMC$SS    [inds]
  MCMCr$sig   <- MCMC$sig   [inds]
  MCMCr$prior <- MCMC$prior [inds]
} 


pairs(MCMCr)
```

\pagebreak

## Misfits

...